Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-24 Methods-and-Results.Rmd
worker descriptives added

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")

@@

histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)

```

@@

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}” (`r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses).

\paragraph{Psychological Needs}

@@

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "purrr",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "misty"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")

@@

# categorical variables:
# - outgroup contact
# - non-outgroup contact

# continuous variables:
# - Core Need fulfillment
# - SDT Competence
# - SDT Autonomy
# - SDT Relatedness
# - Interaction Quality
# - Outgroup Attitudes
######
# within cor
# between cor
# ---
# Grand mean
# SD between
# SD within
# Proportion of variance
# __ __ __
# Note:
# N within ppt.s 
######

# divide into trait and state
dtWorkerSupp$workerWithinBetween <-
  MlTraitState(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection =
      c(
        "keyMotiveFulfilled",
        "competence.daily.all",
        "autonomy.daily.all",
        "relatedness.daily.all",
        "thermometerDutch_1",
        "keymotive_fulfillemt_1",
        "competence_1",
        "autonomy_1",
        "relatedness_1"
      )
  )

workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  save_kable("Tables/workerVarDescr.tex")

workerOutMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

workerOutMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  save_kable("Tables/workerOutVarDescr.tex")

# misty::multilevel.descript(dtWorkerSupp$workerWithinBetween$keyMotiveFulfilled, cluster = dtWorkerSupp$workerWithinBetween$PID)
```

@@

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”. Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
(`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts. These participants are removed from any analyses including outgroup contacts.}.

\paragraph{Psychological Needs} Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment. However, whereas participants with interactions reported on the need fulfillment during the interaction, people without interactions with Dutch people judged the past daytime period in general. To assess the fulfillment of psychological needs, we included two types of need measurement: (1) the core situational need and (2) general self-determination theory needs.

For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”. We then used the participant’s open text entry of their core need to see how much this was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).

We, additionally, included a common measure of three self-determination theory needs \citep[taken from][]{Downie2008}. The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”). All items were rated on a continuous slider scale from very little (-50) to a great deal (+50).

@@

\input{Tables/workerVarDescr}
\input{Tables/workerOutVarDescr}

### 2021-10-24 Methods-and-Results.tex
worker descriptives added

To test the prerequisite effect of intergroup contact, every experience
sampling measurement started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
(31.59\% of all 1225 daily diary responses).

@@

>>>>

To test the prerequisite effect of intergroup contact, every experience
sampling measurement started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
Our participants recorded between 2--51 (3.23--91.07\% of individual
daily diary measurements; 31.59\% of all 1225 daily diary
responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts. These participants are removed from any analyses including outgroup contacts.}.

@@

Irrespective of whether participants had an interaction with Dutch
people or not, everyone answered a short series of questions on
psychological need fulfillment. However, whereas participants with
interactions reported on the need fulfillment during the interaction,
people without interactions with Dutch people judged the past daytime
period in general. To assess the fulfillment of psychological needs, we
included two types of need measurement: (1) the core situational need
and (2) general self-determination theory needs.

For the core situational need, we asked participants in an open ended
text field:
``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
We then used the participant's open text entry of their core need to see
how much this was fulfilled during the interaction or the past daytime
period:
``\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}''
on a continuous slider scale ranging from strongly disagree (-50) to
strongly agree (+50).

We, additionally, included a common measure of three self-determination
theory needs \citep[taken from][]{Downie2008}. The items were introduced
either by ``\textit{During the interaction:}'' or
``\textit{This morning [/afternoon]:}'' and measured autonomy
(``\textit{I was myself.}''), competence
(``\textit{I felt competent.}''), and relatedness (without intergroup
contact ``\textit{I had a strong need to belong}''; with intergroup
contact: ``\textit{I shared information about myself.}'' and
``\textit{The other(s) shared information about themselves.}''). All
items were rated on a continuous slider scale from very little (-50) to
a great deal (+50).

### 2021-10-24 Supplemental-Material-B-Annotated-Analysis.Rmd
worker descriptives added

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")

>>>>

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")

### 2021-10-24 Tables/workerVarDescr.tex
worker descriptives added

\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\begin{tabular}[t]{llcccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
\midrule
Core Need &  & 0.84*** & 0.60*** & 0.27 & -0.02\\
Competence & 0.36*** &  & 0.88*** & 0.17 & -0.24\\
Autonomy & 0.29*** & 0.24*** &  & 0.20 & 0.02\\
Relatedness & 0.50*** & 0.23*** & 0.24*** &  & 0.17\\
Attitudes NL & 0.17** & 0.27*** & 0.27*** & 0.37*** & \\
\addlinespace
Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 72.46\\
Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 13.62\\
Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 9.50\\
ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.68\\
ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.98\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llcccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
\midrule
Core Need &  & 0.67*** & 0.54*** & 0.01 & -0.23\\
Competence & 0.36*** &  & 0.72*** & -0.14 & -0.20\\
Autonomy & 0.31*** & 0.09** &  & -0.05 & 0.19\\
Relatedness & 0.45*** & 0.09** & 0.14*** &  & -0.06\\
Attitudes NL & 0.05 & 0.11*** & 0.12*** & 0.14*** & \\
\addlinespace
Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 71.49\\
Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 12.91\\
Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 8.11\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.99\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{table}
